Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Eliminates addressed comments

  \item {\bf Individual-Individual} The relationships between individuals in the
  population are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be
  of interest, 
  for instance similarity or composition. %This is interesting for
                                %what reason? What do you mean by
                                %composition? "to be composed of"? - JJ

@@

These relations are naturally mapped to graphs, %They are bipartite
                                %graphs, but I don't see your point...
while other actions and 
properties can also be modeled as a semantic network using
basic subject–-predicate-–object expressions
\cite{Prud'hommeaux:14:RT}. % that's a graph, too.. - JJ
Another reason for using a graph model % But for what exactly? A
                                % bipartite graph to express which
                                % relations? - JJ
is the wealth of tools available for
implementing and query the model, and the increased performance of
native graph database systems \cite{holzschuher2013performance,holzschuher2016querying}.

% Moving to related work - Mario
%\cite{Performance for the masses and Christian's previous work},

 % Can it be quantified? Maybe a reference to NodIO? - JJ
%Some authors have already tried to address this basic problem
%\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj
%% Moving this to Related Work Section -Mario
% That section is not there yet. Forgot to paste? - JJ

>>>>

  \item {\bf Individual-Individual} The relationships between individuals in the
  population % do you mean different generations? Would be better to
             % make this more precise - JJ
are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be
  of interest, 
  for instance similarity or composition. %This is interesting for
                                %what reason? What do you mean by
                                %composition? "to be composed of"? - JJ

@@

These relations are naturally mapped to graphs, %They are bipartite
                                %graphs, but I don't see your point...
% Besides, _any_ relation can be mapped to a graph - JJ
while other actions and 
properties can also be modeled as a semantic network using
basic subject–-predicate-–object expressions
\cite{Prud'hommeaux:14:RT}. % that's a graph, too.. - JJ
Another reason for using a graph model % But for what exactly? A
                                % bipartite graph to express which
                                % relations? - JJ
is the wealth of tools available for
implementing and query the model, and the increased performance of
native graph database systems \cite{holzschuher2013performance,holzschuher2016querying}.
